\section{Conclusion and Discussions}

EvoSuite is a very promising automated test case generation tool but it encounters some difficulties during the process.
The generated tests can be obscure to read and various branches may remain uncovered.
The main reason found to have unfulfilled goals comes from a lack of knowledge and ability to reason regarding the internal code structure to generate specific input values required to cover a branch.
If there is a condition for which a specific input value is necessary, EvoSuite occasionally does not find the input value to reach that branch.

This is a limitation of any black-box testing tool, which could be improved by analyzing the source code of the system under test.
These improvements would shift the scope of EvoSuite being a black-box testing tool to a more white-box testing tendency.

But a white-box approach does not solve the problems regarding automated test case generation.
The PrimeChecker CUT shows another difficulty, even when applying white-testing techniques to EvoSuite: it requires a significant amount of resources and time to find the required input value to cover a specific branch, e.g. finding a very large prime number.

The experiment for this research performed an exploratory analysis on the correlations between cyclomatic complexity, code coverage and test readability.
Findings indicate that the cyclomatic complexity of the CUT has no apparent influence on the total branch coverage reached.
Additionally, a weak positive correlation of 0.3044 between cyclomatic complexity and readability of the automatically generated tests is found.
Due to the limited size of the dataset used, no definite conclusion can be drawn from these findings.
However, it does indicate that it might be interesting to pursue an in-depth study on a larger scale that will look at the correlation between cyclomatic complexity and the readability of automatically generated tests.
This target of research could have meaningful implication for the design of test oracles after automated test case generation. 